---
title: "NSTEMI Project"
output: html_notebook
---

```{r Ensure Folders Exist}
Folders_Req <- c("Data", "Normality_Testing", "Table1", "UV_Tables", "MV_Tables", "Cum_Haz_Plots_UnMatched", "CumHazPlots_Bif_True", "CumHazPlots_Bif_False", "CumHazPlots_GT3mm_True", "CumHazPlots_GT3mm_False", "CumHazPlots_GT65_True", "CumHazPlots_GT65_False", "CumHazPlots_Male", "CumHazPlots_Female", "Matching_Files", "Cum_Haz_Plots_Matched", "Cum_Haz_Plots_Matched_BifT", "Cum_Haz_Plots_Matched_BifF", "Cum_Haz_Plots_Matched_GT3mm_T", "Cum_Haz_Plots_Matched_GT3mm_F", "Cum_Haz_Plots_Matched_GT65", "Cum_Haz_Plots_Matched_LT65", "Cum_Haz_Plots_Matched_Male", "Cum_Haz_Plots_Matched_Female")

for (i in 1:length(Folders_Req)) {

if (!dir.exists(paste0(Folders_Req[i]))){
  dir.create(paste0(Folders_Req[i]))
}else{
  print(paste0(Folders_Req[i], " exists"))
}
}

```

```{r Loading Libraries}
library(MatchIt)
library(tidyverse)
library(haven)
library(readxl)
library(gtsummary)
library(rstatix)
library(ggpubr)
library(doParallel)
library(survival)
library(ggpubr)
library(survminer)
library(My.stepwise)
library(gt)

doParallel::registerDoParallel()

theme_gtsummary_journal(journal = "jama")
#> Setting theme `JAMA`
theme_gtsummary_compact()
#> Setting theme `Compact`
```

```{r Columns Handling}
NSTEMI_S <- read_sav("Data/NSTEMI Final File (With Gender!) 25.4.23.sav")

Max_FU_Date = as.POSIXct("2021-03-31", tz = "London/Europe")

NSTEMI <- NSTEMI_S %>%
  transmute(Study_ID = as.numeric(STUDY_ID),
            HospitalNumber = as.numeric(HospitalNumber),
            DCB_DES = factor(DCB1DES2, levels = 1:2, labels = c("DCB", "DES")),
            Procedure_Start = as.POSIXct(PlannedProcedureDatex, tz = "London/Europe"),
            Duration_Procedure =  as.numeric(Durationofprocedure),
            Age = as.numeric(Ageatprocedure),
            Sex = factor(GenderMale1Female2, levels = 1:2, labels = c("Male", "Female")),
            Access = factor(Access.Radial1ulnar2femoral3, levels = 1:3, labels = c("Radial", "Ulna", "Femoral")),
            Pressure_Wire = factor(Pressurewire1, levels = 0:1, labels = c("No", "Yes")),
            Imaging = factor(Imaging.IVUS1OCT2, levels = 1:2, labels = c("IVUS", "OCT")),
            PMHx_Hyperchol = factor(Hypercholesterolaemiafalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_HTN = factor(Hypertensionfalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_PVD = factor(Peripheralvasculardiseasefalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_CVE = factor(Cerebrovasculareventfalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_Transplant = factor(Cardiactransplantfalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_MI = factor(MIfalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_PCI = factor(PCIfalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_CABG = factor(CABGfalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_HF = factor(HeartFailurefalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_AF = factor(AF, levels = 0:1, labels = c("No", "Yes")),
            FHx_CAD = factor(FamilyHistoryofCADfalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_COPD = factor(COPDfalse0true1, levels = 0:1, labels = c("No", "Yes")),
            PMHx_DM = factor(Diabetesno0yes1, levels = 0:1, labels = c("No", "Yes")),
            Smok_Stat = factor(smokingstatusneversmoked0currentexsmoker1, levels = 0:1, labels = c("Never Smoked", "Current/Ex Smoker")),
            GFR = as.numeric(parse_number(ResulteGFR)),
            Creatinine = as.numeric(CreatinineLevel245),
            Vessel_Tx = factor(VesseltreatedinnumbersLMS1LAD2LCx3RCA4Graft5, levels = 1:5, labels = c("LMS", "LAD", "LCx", "RCA", "Graft")),
            LMSLAD_VesselTx = factor(case_when(Vessel_Tx == "LMS|LAD" ~ 1, T ~ 0), levels = 0:1, labels = c("No", "LMS/LAD")),
            LMS_VesselTx = factor(case_when(Vessel_Tx == "LMS" ~ 1, T ~ 0), levels = 0:1, labels = c("No", "LMS")),
            Multivessel_VesselTx = factor(MultivesselPCI, levels = 0:1, labels = c("No", "Multivessel PCI")),
            denovo_VesselDiam = as.numeric(Vesseldiameter),
            denovo_LesionLgth = as.numeric(LesionLength),
            Vessel_GT3mm = factor(case_when(denovo_LesionLgth >30 ~ 1, T ~ 0), levels = 0:1, labels = c("No", "Yes")),
            Tash_Bif = factor(Bifurcation, levels = 0:1, labels = c("No", "Yes")),
            Coronary_Dissection = factor(Dissectionno_0A_1B_2C_3, levels = 1:3, labels = c("Type A", "Type B", "Type C")),
            Frailty_Sc = as.numeric(frailty),
            Frailty_Bin = factor(group, levels = 0:1, labels = c("Not Frail", "Frail")),
            Heavy_Calc = factor(Heavycalcification, levels = 0:1, labels = c("No", "Yes")),
            Diffuse_Dx = factor(Diffusedisease, levels = 0:1, labels = c("No", "Yes")),
            Tortuosity = factor(Tortuosity, levels = 0:1, labels = c("No", "Yes")),
            Hb = as.numeric(parse_number(Haemoglobin)),
            Lym = as.numeric(ResultLymphocytes),
            Neu = as.numeric(ResultNeutrophils),
            WBC = as.numeric(Neu+Lym),
            Creatinine = as.numeric(CreatinineLevel245),
            Anaemia_Acuity = case_when(Sex == "Male" & Hb < 130 ~ 6,
                                  Sex == "Female" & Hb < 120 ~ 6,
                                  TRUE ~ 0),
            Gender_Acuity = case_when(Sex == "Male" ~ 0,
                                      Sex == "Female" ~ 8,
                                      TRUE ~ NA_real_),
            Age_Acuity = case_when(Age < 50 ~ 0,
                                   Age>=50 & Age<60 ~ 3,
                                   Age>=60 & Age<70 ~ 6,
                                   Age>=70 & Age<80 ~ 9,
                                   Age>= 80 ~ 12,
                                   TRUE ~ NA_real_),
            Creatinine_Acuity = case_when(Creatinine < 1.0 ~ 0,
                                          Creatinine>=1.0 & Creatinine<1.2 ~ 2,
                                          Creatinine>=1.2 & Creatinine<1.4 ~ 3,
                                          Creatinine>=1.4 & Creatinine<1.6 ~ 5,
                                          Creatinine>=1.6 & Creatinine<1.8 ~ 6,
                                          Creatinine>=1.8 & Creatinine<2.0 ~ 8,
                                          Creatinine>=2.0 ~ 10,
                                          TRUE ~ NA_real_),
            WBC_Acuity = case_when(WBC < 10 ~ 0,
                                   WBC>=10 & WBC<12 ~ 2,
                                   WBC>=12 & WBC<14 ~ 3,
                                   WBC>=14 & WBC<16 ~ 5,
                                   WBC>=16 & WBC<18 ~ 6,
                                   WBC>=18 & WBC<20 ~ 8,
                                   WBC>=20 ~ 10,
                                   TRUE ~ NA_real_),
            Presentation_Acuity = case_when(TRUE ~ 6),
            Antithrombotic_Acuity = case_when(TRUE ~ 0),
            Acuity_Sc = Anaemia_Acuity + Gender_Acuity + Age_Acuity + Creatinine_Acuity + WBC_Acuity + Presentation_Acuity + Antithrombotic_Acuity,
            Max_FU = as.numeric(difftime(Max_FU_Date, Procedure_Start, units = "days")),
            Mortality = as.numeric(Death),
            Mortality_FU = as.numeric(TimetoMortality),
            Mortality_FU365 = pmin(Mortality_FU, 365),
            Mortality_365 = case_when(Mortality_FU365 < 365 & Mortality == 1 ~ 1,
                                      TRUE ~ 0),
            Mortality_FU30 = pmin(Mortality_FU, 30),
            Mortality_30 = case_when(Mortality_FU30 < 30 & Mortality == 1 ~ 1,
                                      TRUE ~ 0),
            CV_Mortality = as.numeric(Cardiacdeath),
            CV_Mortality_FU = case_when(CV_Mortality == 1 ~ Mortality_FU,
                                     TRUE ~ Max_FU),
            CV_Mortality_FU365 = pmin(CV_Mortality_FU, 365),
            CV_Mortality_365 = case_when(CV_Mortality_FU365 < 365 & CV_Mortality == 1 ~ 1,
                                      TRUE ~ 0),
            CV_Mortality_FU30 = pmin(CV_Mortality_FU, 30),
            CV_Mortality_30 = case_when(CV_Mortality_FU30 < 30 & CV_Mortality == 1 ~ 1,
                                      TRUE ~ 0),
            TIA = as.numeric(CVA),
            TIA_FU = as.numeric(TimetoCVA),
            TIA_FU365 = pmin(TIA_FU, 365),
            TIA_365 = case_when(TIA_FU365 < 365 & TIA == 1 ~ 1,
                                      TRUE ~ 0),
            TIA_FU30 = pmin(TIA_FU, 30),
            TIA_30 = case_when(TIA_FU30 < 30 & TIA == 1 ~ 1,
                                      TRUE ~ 0),
            
            ACS = as.numeric(ACS),
            ACS_FU = as.numeric(TimetoACS),
            ACS_FU365 = pmin(ACS_FU, 365),
            ACS_365 = case_when(ACS_FU365 < 365 & ACS == 1 ~ 1,
                                      TRUE ~ 0),
            ACS_FU30 = pmin(ACS_FU, 30),
            ACS_30 = case_when(ACS_FU30 < 30 & ACS == 1 ~ 1,
                                      TRUE ~ 0),
            
            MajBleeding = as.numeric(Bleeding),
            MajBleeding_FU = as.numeric(TimetoBleeding),
            MajBleeding_FU365 = pmin(MajBleeding_FU, 365),
            MajBleeding_365 = case_when(MajBleeding_FU365 < 365 & MajBleeding == 1 ~ 1,
                                      TRUE ~ 0),
            MajBleeding_FU30 = pmin(MajBleeding_FU, 30),
            MajBleeding_30 = case_when(MajBleeding_FU30 < 30 & MajBleeding == 1 ~ 1),
            
            Composite_wMort =case_when(Mortality == 1 ~ 1,
                                  CV_Mortality == 1 ~ 1,
                                  TIA == 1 ~ 1,
                                  ACS == 1 ~ 1,
                                  MajBleeding == 1 ~ 1,
                                  TRUE ~ 0),
            Composite_wMort_FU = case_when(Composite_wMort == T ~ pmin(Mortality_FU, CV_Mortality_FU, TIA_FU, ACS_FU, MajBleeding_FU),
                                     TRUE ~ Max_FU),
            Composite_wMort_FU365 = pmin(Composite_wMort_FU, 365),
            Composite_wMort_365 = case_when(Composite_wMort_FU365 < 365 & Composite_wMort == 1 ~ 1,
                                      TRUE ~ 0),
            Composite_wMort_FU30 = pmin(Composite_wMort_FU, 30),
            Composite_wMort_30 = case_when(Composite_wMort_FU30 < 30 & Composite_wMort == 1 ~ 1))
```

```{r Normality Testing}
NumVar <- NSTEMI %>%
  select(where(is.numeric)) %>%
  select(3:21, -ends_with("Acuity")) %>%
  names() %>%
  syms()

Shapiro_Test <- NSTEMI %>%
  shapiro_test(vars = NumVar) 

NormallyDistVars <- Shapiro_Test %>%
  filter(p >= 0.05) %>%
  pull(variable) 

NonNormallyDistVars <- Shapiro_Test %>%
  filter(p < 0.05) %>%
  pull(variable) 

non_normal_densityplots <- list()
non_normal_qqplots <- list()

for (i in 1:length(NonNormallyDistVars)) {
  
  non_normal_densityplots[[i]] <- NSTEMI %>%
  ggdensity(NonNormallyDistVars[i], fill = "lightgray") 
  
  non_normal_qqplots[[i]] <- NSTEMI %>%
  ggqqplot(NonNormallyDistVars[i], fill = "lightgray") 
  
}

ggexport(plotlist = non_normal_densityplots, filename = "Normality_Testing/density.pdf",
         nrow = 2, ncol = 2)

ggexport(plotlist = non_normal_qqplots, filename = "Normality_Testing/qq.pdf",
         nrow = 2, ncol = 2)

NormallyDistVars <-  c()
```

```{r Table 1}
NSTEMI_Table <- NSTEMI %>%
  select(-ends_with("Acuity"))

Baseline_T <- tbl_summary(NSTEMI_Table,
            by = DCB_DES) %>%
  add_p() %>%
  bold_p() %>%
  add_overall() %>%
  gtsummary::separate_p_footnotes() %>%
  as_gt() 

gtsave(Baseline_T, "Table1/BaselineT.html")
```

```{r Univariate Tables}
UV_T <- list()

Outcomes <- c("Mortality", "CV_Mortality", "ACS", "MajBleeding", "TIA", "Composite_wMort")
Followups <- c("Mortality_FU", "CV_Mortality_FU", "ACS_FU", "MajBleeding_FU", "TIA_FU", "Composite_wMort_FU")

library(doFuture)
registerDoFuture()
plan(multisession)

foreach(i=1:6, .packages = c("foreach", "tidyverse", "gtsummary")) %dopar% {
  
theme_gtsummary_journal(journal = "jama")
#> Setting theme `JAMA`
theme_gtsummary_compact()
#> Setting theme `Compact`

.GlobalEnv$UV_T[[i]] <- gtsummary::tbl_uvregression(NSTEMI,
                 method = survival::coxph,
                 y = survival::Surv(time = !!sym(Followups[i]), event = !!sym(Outcomes[i])),
                 exponentiate = T,
                 include = c(DCB_DES, Age, Sex, dplyr::starts_with("PMHx"), FHx_CAD, Smok_Stat, GFR, Creatinine, Vessel_Tx, LMSLAD_VesselTx, LMS_VesselTx, Multivessel_VesselTx, denovo_VesselDiam, denovo_LesionLgth, Vessel_GT3mm, Tash_Bif, Coronary_Dissection, Diffuse_Dx, Tortuosity, Frailty_Sc, Frailty_Bin, Heavy_Calc, Hb, Lym, Neu, WBC, ends_with("Acuity"), Acuity_Sc)) %>%
  modify_header(label = paste0("**",Outcomes[i],"**", " (Univariate)")) %>%
  bold_p() %>%
  as_gt()

gt::gtsave(.GlobalEnv$UV_T[[i]], paste0("UV_Tables/" , Outcomes[i], "_UV.html"))

}
```

```{r CumHaz Charts Part 1 (all, 365, 30)}
fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = NSTEMI)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = NSTEMI)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = NSTEMI)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = NSTEMI)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = NSTEMI)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring CVA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = NSTEMI)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_UnMatched/CumHazPlots.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = NSTEMI)
plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = NSTEMI)
plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = NSTEMI)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = NSTEMI)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = NSTEMI)
plot5<- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring CVA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = NSTEMI)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")


cairo_pdf(filename = "Cum_Haz_Plots_UnMatched/CumHazPlots365.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = NSTEMI)
plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = NSTEMI)
plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = NSTEMI)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = NSTEMI)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30,TIA_30) ~ DCB_DES, data = NSTEMI)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = NSTEMI)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_UnMatched/CumHazPlots30.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()
```

```{r Cum Haz Charts Bifurcation Y Part 2 (all, 365, 30)}
NSTEMI_Bif <- NSTEMI %>%
  filter(Tash_Bif == "Yes")

fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = NSTEMI_Bif)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = NSTEMI_Bif)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = NSTEMI_Bif)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = NSTEMI_Bif)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = NSTEMI_Bif)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = NSTEMI_Bif)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_Bif_True/CumHazPlots_Bif.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = NSTEMI_Bif)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = NSTEMI_Bif)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = NSTEMI_Bif)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = NSTEMI_Bif)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = NSTEMI_Bif)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "") 

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = NSTEMI_Bif)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_Bif_True/CumHazPlots_Bif_365.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = NSTEMI_Bif)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = NSTEMI_Bif)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = NSTEMI_Bif)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = NSTEMI_Bif)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = NSTEMI_Bif)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = NSTEMI_Bif)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")


cairo_pdf(filename = "CumHazPlots_Bif_True/CumHazPlots_Bif_30.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()
```

```{r Cum Haz Bifurcation N Part 3 (all, 365, 30)}
NSTEMI_Bif <- NSTEMI %>%
  filter(Tash_Bif == "No")

fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = NSTEMI_Bif)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = NSTEMI_Bif)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = NSTEMI_Bif)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = NSTEMI_Bif)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = NSTEMI_Bif)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = NSTEMI_Bif)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_Bif_False/CumHazPlots_Bif_No.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = NSTEMI_Bif)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = NSTEMI_Bif)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = NSTEMI_Bif)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = NSTEMI_Bif)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = NSTEMI_Bif)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = NSTEMI_Bif)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_Bif_False/CumHazPlots_Bif_No_365.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = NSTEMI_Bif)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = NSTEMI_Bif)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = NSTEMI_Bif)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = NSTEMI_Bif)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = NSTEMI_Bif)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = NSTEMI_Bif)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_Bif_False/CumHazPlots_Bif_No_30.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()
```

```{r Cum Haz GTE3 length Y Part 4 (all, 365, 30)}
NSTEMI_GT3mm <- NSTEMI %>%
  filter(Vessel_GT3mm == "Yes")

fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = NSTEMI_GT3mm)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = NSTEMI_GT3mm)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = NSTEMI_GT3mm)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = NSTEMI_GT3mm)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = NSTEMI_GT3mm)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = NSTEMI_GT3mm)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_GT3mm_True/CumHazPlots_GT3mm.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")


cairo_pdf(filename = "CumHazPlots_GT3mm_True/CumHazPlots_GT3mm_365.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")


cairo_pdf(filename = "CumHazPlots_GT3mm_True/CumHazPlots_GT3mm_30.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()
```

```{r Cum Haz GTE3 length N Part 5 (all, 365, 30)}
NSTEMI_GT3mm <- NSTEMI %>%
  filter(Vessel_GT3mm == "No")

fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = NSTEMI_GT3mm)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = NSTEMI_GT3mm)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = NSTEMI_GT3mm)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = NSTEMI_GT3mm)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = NSTEMI_GT3mm)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = NSTEMI_GT3mm)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")


cairo_pdf(filename = "CumHazPlots_GT3mm_False/CumHazPlots_GT3mm_No.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = NSTEMI_GT3mm)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")


cairo_pdf(filename = "CumHazPlots_GT3mm_False/CumHazPlots_GT3mm_No_365.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = NSTEMI_GT3mm)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")


cairo_pdf(filename = "CumHazPlots_GT3mm_False/CumHazPlots_GT3mm_No_30.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()
```

```{r Cum Haz Male Part 4 (all, 365, 30)}
NSTEMI_Sex <- NSTEMI %>%
  filter(Sex == "Male")

fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = NSTEMI_Sex)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = NSTEMI_Sex)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = NSTEMI_Sex)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = NSTEMI_Sex)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = NSTEMI_Sex)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = NSTEMI_Sex)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")


cairo_pdf(filename = "CumHazPlots_Male/CumHazPlots_Male.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = NSTEMI_Sex)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = NSTEMI_Sex)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = NSTEMI_Sex)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = NSTEMI_Sex)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = NSTEMI_Sex)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = NSTEMI_Sex)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_Male/CumHazPlots_Male_365.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = NSTEMI_Sex)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = NSTEMI_Sex)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = NSTEMI_Sex)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = NSTEMI_Sex)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = NSTEMI_Sex)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = NSTEMI_Sex)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_Male/CumHazPlots_Male_30.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()
```

```{r Cum Haz Female Part 5 (all, 365, 30)}
NSTEMI_Sex <- NSTEMI %>%
  filter(Sex == "Female")

fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = NSTEMI_Sex)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = NSTEMI_Sex)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = NSTEMI_Sex)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = NSTEMI_Sex)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = NSTEMI_Sex)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = NSTEMI_Sex)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_Female/CumHazPlots_Female.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = NSTEMI_Sex)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = NSTEMI_Sex)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = NSTEMI_Sex)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = NSTEMI_Sex)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = NSTEMI_Sex)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = NSTEMI_Sex)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_Female/CumHazPlots_Female_365.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = NSTEMI_Sex)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = NSTEMI_Sex)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = NSTEMI_Sex)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = NSTEMI_Sex)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = NSTEMI_Sex)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_Female/CumHazPlots_Female_30.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
#print(plot4)
print(plot5)
print(plot6)
dev.off()
```

```{r Cum Haz Age >65 Part 4 (all, 365, 30)}
NSTEMI_Age <- NSTEMI %>%
  filter(Age >= 65)

fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = NSTEMI_Age)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = NSTEMI_Age)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = NSTEMI_Age)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = NSTEMI_Age)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = NSTEMI_Age)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = NSTEMI_Age)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_GT65_True/CumHazPlots_GT65.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = NSTEMI_Age)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = NSTEMI_Age)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = NSTEMI_Age)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = NSTEMI_Age)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = NSTEMI_Age)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = NSTEMI_Age)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_GT65_True/CumHazPlots_GT65_365.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = NSTEMI_Age)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = NSTEMI_Age)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = NSTEMI_Age)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = NSTEMI_Age)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = NSTEMI_Age)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = NSTEMI_Age)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_GT65_True/CumHazPlots_GT65_30.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()
```

```{r Cum Haz Age <65 Part 5 (all, 365, 30)}
NSTEMI_Age <- NSTEMI %>%
  filter(Age < 65)

fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = NSTEMI_Age)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = NSTEMI_Age)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = NSTEMI_Age)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = NSTEMI_Age)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = NSTEMI_Age)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = NSTEMI_Age)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_GT65_False/CumHazPlots_GT65.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = NSTEMI_Age)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = NSTEMI_Age)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = NSTEMI_Age)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = NSTEMI_Age)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = NSTEMI_Age)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = NSTEMI_Age)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_GT65_False/CumHazPlots_GT65_365.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = NSTEMI_Age)
plot1 <- ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = NSTEMI_Age)
plot2 <- ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = NSTEMI_Age)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = NSTEMI_Age)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.2), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = NSTEMI_Age)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "CumHazPlots_GT65_False/CumHazPlots_GT65_30.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot5)
print(plot6)
dev.off()
```

```{r Multivariate for All Outcomes}
library(furrr)

MV_T <- list()

Outcomes <- c("Mortality", "CV_Mortality", "ACS", "MajBleeding", "TIA", "Composite_wMort")
Followups <- c("Mortality_FU", "CV_Mortality_FU", "ACS_FU", "MajBleeding_FU", "TIA_FU", "Composite_wMort_FU")

doParallel::registerDoParallel()

NSTEMI_Mort <- NSTEMI %>%
  select(DCB_DES, Age, PMHx_PVD, PMHx_CVE, PMHx_MI, PMHx_PCI, PMHx_CABG, PMHx_HF, PMHx_AF, FHx_CAD, PMHx_COPD, PMHx_DM, GFR, LMS_VesselTx, Multivessel_VesselTx, Frailty_Sc, Heavy_Calc, Acuity_Sc, Mortality, Mortality_FU, CV_Mortality, CV_Mortality_FU, ACS, ACS_FU, MajBleeding, MajBleeding_FU, TIA, TIA_FU, Composite_wMort, Composite_wMort_FU) %>%
  drop_na()

set.seed(123)  

res.cox <- future_map(Outcomes, ~coxph(as.formula(paste0("Surv(time = ",.x ,"_FU", ", event = ", .x, ") ~  DCB_DES +  Age + PMHx_PVD + PMHx_CVE + PMHx_MI + PMHx_PCI + PMHx_CABG + PMHx_HF + PMHx_AF + FHx_CAD + PMHx_COPD + PMHx_DM + GFR + LMS_VesselTx + Multivessel_VesselTx + Frailty_Sc + Heavy_Calc + Acuity_Sc")), data =  NSTEMI_Mort)) 

step_reg <- map(1:6, ~stats::step(res.cox[[.x]], direction='both', scope=list(lower = Surv(time = !!sym(Followups[.x]), event = !!sym(Outcomes[.x])) ~ DCB_DES, upper = stats::formula(res.cox[[.x]])), trace=0))

MV_T <- map(1:6, ~gtsummary::tbl_regression(step_reg[[.x]], 
               exponentiate = T, 
               #show_single_row = c(DCB_DES, PMHx_CVE, PMHx_HF, FHx_CAD),
               #label = list(DCB_DES ~ "DCB/DES [DES]",
                       #      PMHx_CVE ~ "History of Cerebrovascular Events",
                       #      PMHx_HF ~ "History of Heart Failure",
                       #      FHx_CAD ~ "Family History of Coronary Artery Disease",
                       #      GFR ~ "eGFR",
                          #   Frailty_Sc ~ "Frailty Score")
               ) %>%
  gtsummary::bold_p() %>%
  gtsummary::modify_header(label = paste0("**",Outcomes[.x],"**", " (Multivariate)")) %>%
  gtsummary::add_n() %>%
  gtsummary::as_gt())

map(1:6, ~gt::gtsave(MV_T[[.x]], paste0("MV_Tables/" , Outcomes[.x], "_MV.html")))

```

The choice between Mahalanobis distance and logit distance depends on the specific context and goals of the analysis. Both distance metrics have their advantages and considerations:

Mahalanobis distance:

Mahalanobis distance takes into account the covariance structure between covariates, which allows for capturing the correlations among variables. It can be particularly useful when there are strong interdependencies between the covariates.
It is a robust distance metric that is not affected by changes in scale or units of measurement.
Mahalanobis distance can handle continuous, categorical, or mixed-type covariates without requiring any specific transformations.
However, computing Mahalanobis distance can be computationally expensive, especially with large datasets, due to the need to calculate the covariance matrix.
Logit distance:

Logit distance is based on the estimated propensity scores from a logistic regression model. It measures the difference in log-odds of being in the treated group between pairs of observations.
Logit distance is relatively straightforward to compute and interpret, and it is commonly used in propensity score matching studies.
It does not explicitly account for correlations between covariates, which may be a limitation if there are strong interdependencies among the variables.
Logit distance assumes linearity in the log-odds relationship, which may not hold in all cases.


In summary, the choice between Mahalanobis distance and logit distance depends on factors such as the nature of the data, the presence of correlations between covariates, and the computational considerations. It is recommended to compare the results obtained using different distance metrics and assess their impact on the matching quality and treatment effect estimates to determine which distance metric performs better in a given analysis.

```{r Searching for the variables to PS Match for}
PS_Variable_Search <- NSTEMI %>%
  drop_na(DCB_DES) %>%
  select(-Study_ID, -HospitalNumber, -Procedure_Start, -Imaging, -LMSLAD_VesselTx)

gtsummary::tbl_uvregression(PS_Variable_Search,
                 method = glm,
                 method.args = list(family = binomial),
                 y = DCB_DES,
                 exponentiate = T) %>%
  modify_header(label = paste0("**",Outcomes[i],"**", " (Univariate)")) %>%
  bold_p() %>%
  as_gt()

PS_Variables = c("DCB_DES", "Duration_Procedure", "PMHx_AF", "FHx_CAD", "denovo_VesselDiam", "denovo_LesionLgth", "Tash_Bif", "Diffuse_Dx", "Tortuosity")
```

```{r PS Matching (All)}
NSTEMI_PS_Mort <- NSTEMI %>%
  select(DCB_DES, Age, Sex, PMHx_AF, FHx_CAD, Tash_Bif, Diffuse_Dx, Tortuosity, denovo_LesionLgth, denovo_VesselDiam, Mortality, Mortality_FU, Mortality_FU365, Mortality_365, Mortality_FU30, Mortality_30, CV_Mortality, CV_Mortality_FU, CV_Mortality_FU365, CV_Mortality_365, CV_Mortality_FU30,CV_Mortality_30, ACS, ACS_FU, ACS_FU365, ACS_365, ACS_FU30, ACS_30, TIA, TIA_FU, TIA_FU365, TIA_365, TIA_FU30, TIA_30, MajBleeding, MajBleeding_FU, MajBleeding_FU365, MajBleeding_365, MajBleeding_FU30, MajBleeding_30, Composite_wMort, Composite_wMort_FU, Composite_wMort_FU365, Composite_wMort_365, Composite_wMort_FU30, Composite_wMort_30) %>%
  drop_na(1:10)

set.seed(1234)

match.it <- matchit(DCB_DES ~ Age+ Sex + PMHx_AF+ FHx_CAD+ Tash_Bif+ Diffuse_Dx+ Tortuosity+ denovo_LesionLgth+ denovo_VesselDiam, data = NSTEMI_PS_Mort,  method="genetic", replace = T,  pop.size = 1000)
a <- summary(match.it)

#create new dataframe without unmatched
df.match1 <- get_matches(match.it)

write_csv(df.match1, "Data/PS_Match_All.csv")

df.match_All <- df.match1
```

```{r PS Matching (Bifur T)}
NSTEMI2 <- NSTEMI %>%
  filter(Tash_Bif == "Yes")

NSTEMI_PS_Mort <- NSTEMI2 %>%
  select(DCB_DES, Age, Sex, PMHx_AF, FHx_CAD, Tash_Bif, Diffuse_Dx, Tortuosity, denovo_LesionLgth, denovo_VesselDiam, Mortality, Mortality_FU, Mortality_FU365, Mortality_365, Mortality_FU30, Mortality_30, CV_Mortality, CV_Mortality_FU, CV_Mortality_FU365, CV_Mortality_365, CV_Mortality_FU30,CV_Mortality_30, ACS, ACS_FU, ACS_FU365, ACS_365, ACS_FU30, ACS_30, TIA, TIA_FU, TIA_FU365, TIA_365, TIA_FU30, TIA_30, MajBleeding, MajBleeding_FU, MajBleeding_FU365, MajBleeding_365, MajBleeding_FU30, MajBleeding_30, Composite_wMort, Composite_wMort_FU, Composite_wMort_FU365, Composite_wMort_365, Composite_wMort_FU30, Composite_wMort_30) %>%
  drop_na(1:10)

set.seed(1234)

match.it <- matchit(DCB_DES ~ Age+ Sex + PMHx_AF+ FHx_CAD+ Diffuse_Dx+ Tortuosity+ denovo_LesionLgth+ denovo_VesselDiam, data = NSTEMI_PS_Mort,  method="genetic", replace = T,  pop.size = 1000)
a <- summary(match.it)

#create new dataframe without unmatched
df.match1 <- get_matches(match.it)

df.match1_BifT <- df.match1
```

```{r PS Matching (Bifur F)}

NSTEMI2 <- NSTEMI %>%
  filter(Tash_Bif == "No")

NSTEMI_PS_Mort <- NSTEMI2 %>%
  select(DCB_DES, Age, Sex, PMHx_AF, FHx_CAD, Tash_Bif, Diffuse_Dx, Tortuosity, denovo_LesionLgth, denovo_VesselDiam, Mortality, Mortality_FU, Mortality_FU365, Mortality_365, Mortality_FU30, Mortality_30, CV_Mortality, CV_Mortality_FU, CV_Mortality_FU365, CV_Mortality_365, CV_Mortality_FU30,CV_Mortality_30, ACS, ACS_FU, ACS_FU365, ACS_365, ACS_FU30, ACS_30, TIA, TIA_FU, TIA_FU365, TIA_365, TIA_FU30, TIA_30, MajBleeding, MajBleeding_FU, MajBleeding_FU365, MajBleeding_365, MajBleeding_FU30, MajBleeding_30, Composite_wMort, Composite_wMort_FU, Composite_wMort_FU365, Composite_wMort_365, Composite_wMort_FU30, Composite_wMort_30) %>%
  drop_na(1:10)

set.seed(1234)

match.it <- matchit(DCB_DES ~ Age+ Sex + PMHx_AF+ FHx_CAD+ Diffuse_Dx+ Tortuosity+ denovo_LesionLgth+ denovo_VesselDiam, data = NSTEMI_PS_Mort,  method="genetic", replace = T,  pop.size = 1000)
a <- summary(match.it)

df.match1 <- get_matches(match.it)

df.match1_BifF <- df.match1
```

```{r PS Matching (GT3mm T)}
NSTEMI2 <- NSTEMI %>%
  filter(Vessel_GT3mm == "Yes")

NSTEMI_PS_Mort <- NSTEMI2 %>%
  select(DCB_DES, Age, Sex, PMHx_AF, FHx_CAD, Tash_Bif, Diffuse_Dx, Tortuosity, denovo_LesionLgth, denovo_VesselDiam, Mortality, Mortality_FU, Mortality_FU365, Mortality_365, Mortality_FU30, Mortality_30, CV_Mortality, CV_Mortality_FU, CV_Mortality_FU365, CV_Mortality_365, CV_Mortality_FU30,CV_Mortality_30, ACS, ACS_FU, ACS_FU365, ACS_365, ACS_FU30, ACS_30, TIA, TIA_FU, TIA_FU365, TIA_365, TIA_FU30, TIA_30, MajBleeding, MajBleeding_FU, MajBleeding_FU365, MajBleeding_365, MajBleeding_FU30, MajBleeding_30, Composite_wMort, Composite_wMort_FU, Composite_wMort_FU365, Composite_wMort_365, Composite_wMort_FU30, Composite_wMort_30) %>%
  drop_na(1:10)

set.seed(1234)

match.it <- matchit(DCB_DES ~ Age+ Sex + PMHx_AF+ FHx_CAD+ Tash_Bif+ Diffuse_Dx+ Tortuosity+ denovo_LesionLgth+ denovo_VesselDiam, data = NSTEMI_PS_Mort,  method="genetic", replace = T,  pop.size = 1000)
a <- summary(match.it)

df.match1 <- get_matches(match.it)

df.match1_GT3mmT <- df.match1
```

```{r PS Matching (GT3mm F)}

NSTEMI2 <- NSTEMI %>%
  filter(Vessel_GT3mm == "No")

NSTEMI_PS_Mort <- NSTEMI2 %>%
  select(DCB_DES, Age, Sex, PMHx_AF, FHx_CAD, Tash_Bif, Diffuse_Dx, Tortuosity, denovo_LesionLgth, denovo_VesselDiam, Mortality, Mortality_FU, Mortality_FU365, Mortality_365, Mortality_FU30, Mortality_30, CV_Mortality, CV_Mortality_FU, CV_Mortality_FU365, CV_Mortality_365, CV_Mortality_FU30,CV_Mortality_30, ACS, ACS_FU, ACS_FU365, ACS_365, ACS_FU30, ACS_30, TIA, TIA_FU, TIA_FU365, TIA_365, TIA_FU30, TIA_30, MajBleeding, MajBleeding_FU, MajBleeding_FU365, MajBleeding_365, MajBleeding_FU30, MajBleeding_30, Composite_wMort, Composite_wMort_FU, Composite_wMort_FU365, Composite_wMort_365, Composite_wMort_FU30, Composite_wMort_30) %>%
  drop_na(1:10)

set.seed(1234)

match.it <- matchit(DCB_DES ~ Age+ Sex + PMHx_AF+ FHx_CAD+ Tash_Bif+ Diffuse_Dx+ Tortuosity+ denovo_LesionLgth+ denovo_VesselDiam, data = NSTEMI_PS_Mort,  method="genetic", replace = T,  pop.size = 1000)
a <- summary(match.it)

df.match1 <- get_matches(match.it)

df.match1_GT3mmF <- df.match1
```

```{r PS Matching (Male)}

NSTEMI2 <- NSTEMI %>%
  filter(Sex == "Male")

NSTEMI_PS_Mort <- NSTEMI2 %>%
  select(DCB_DES, Age, Sex, PMHx_AF, FHx_CAD, Tash_Bif, Diffuse_Dx, Tortuosity, denovo_LesionLgth, denovo_VesselDiam, Mortality, Mortality_FU, Mortality_FU365, Mortality_365, Mortality_FU30, Mortality_30, CV_Mortality, CV_Mortality_FU, CV_Mortality_FU365, CV_Mortality_365, CV_Mortality_FU30,CV_Mortality_30, ACS, ACS_FU, ACS_FU365, ACS_365, ACS_FU30, ACS_30, TIA, TIA_FU, TIA_FU365, TIA_365, TIA_FU30, TIA_30, MajBleeding, MajBleeding_FU, MajBleeding_FU365, MajBleeding_365, MajBleeding_FU30, MajBleeding_30, Composite_wMort, Composite_wMort_FU, Composite_wMort_FU365, Composite_wMort_365, Composite_wMort_FU30, Composite_wMort_30) %>%
  drop_na(1:10)

set.seed(1234)

match.it <- matchit(DCB_DES ~ Age + PMHx_AF+ FHx_CAD+ Tash_Bif+ Diffuse_Dx+ Tortuosity+ denovo_LesionLgth+ denovo_VesselDiam, data = NSTEMI_PS_Mort,  method="genetic", replace = T,  pop.size = 1000)
a <- summary(match.it)

df.match1 <- get_matches(match.it)

df.match1_Male <- df.match1
```

```{r PS Matching (Female)}

NSTEMI2 <- NSTEMI %>%
  filter(Sex == "Female")

NSTEMI_PS_Mort <- NSTEMI2 %>%
  select(DCB_DES, Age, Sex, PMHx_AF, FHx_CAD, Tash_Bif, Diffuse_Dx, Tortuosity, denovo_LesionLgth, denovo_VesselDiam, Mortality, Mortality_FU, Mortality_FU365, Mortality_365, Mortality_FU30, Mortality_30, CV_Mortality, CV_Mortality_FU, CV_Mortality_FU365, CV_Mortality_365, CV_Mortality_FU30,CV_Mortality_30, ACS, ACS_FU, ACS_FU365, ACS_365, ACS_FU30, ACS_30, TIA, TIA_FU, TIA_FU365, TIA_365, TIA_FU30, TIA_30, MajBleeding, MajBleeding_FU, MajBleeding_FU365, MajBleeding_365, MajBleeding_FU30, MajBleeding_30, Composite_wMort, Composite_wMort_FU, Composite_wMort_FU365, Composite_wMort_365, Composite_wMort_FU30, Composite_wMort_30) %>%
  drop_na(1:10)

set.seed(1234)

match.it <- matchit(DCB_DES ~ Age + PMHx_AF+ FHx_CAD+ Tash_Bif+ Diffuse_Dx+ Tortuosity+ denovo_LesionLgth+ denovo_VesselDiam, data = NSTEMI_PS_Mort,  method="genetic", replace = T,  pop.size = 1000)
a <- summary(match.it)

df.match1 <- get_matches(match.it)

df.match1_Female <- df.match1
```

```{r PS Matching (GT65)}

NSTEMI2 <- NSTEMI %>%
  filter(Age >= 65)

NSTEMI_PS_Mort <- NSTEMI2 %>%
  select(DCB_DES, Age, Sex, PMHx_AF, FHx_CAD, Tash_Bif, Diffuse_Dx, Tortuosity, denovo_LesionLgth, denovo_VesselDiam, Mortality, Mortality_FU, Mortality_FU365, Mortality_365, Mortality_FU30, Mortality_30, CV_Mortality, CV_Mortality_FU, CV_Mortality_FU365, CV_Mortality_365, CV_Mortality_FU30,CV_Mortality_30, ACS, ACS_FU, ACS_FU365, ACS_365, ACS_FU30, ACS_30, TIA, TIA_FU, TIA_FU365, TIA_365, TIA_FU30, TIA_30, MajBleeding, MajBleeding_FU, MajBleeding_FU365, MajBleeding_365, MajBleeding_FU30, MajBleeding_30, Composite_wMort, Composite_wMort_FU, Composite_wMort_FU365, Composite_wMort_365, Composite_wMort_FU30, Composite_wMort_30) %>%
  drop_na(1:10)

set.seed(1234)

match.it <- matchit(DCB_DES ~ Age+ Sex + PMHx_AF+ FHx_CAD+ Tash_Bif+ Diffuse_Dx+ Tortuosity+ denovo_LesionLgth+ denovo_VesselDiam, data = NSTEMI_PS_Mort,  method="genetic", replace = T,  pop.size = 1000)
a <- summary(match.it)

df.match1 <- get_matches(match.it)

df.match1_GT65 <- df.match1
```

```{r PS Matching (LT65)}

NSTEMI2 <- NSTEMI %>%
  filter(Age < 65)

NSTEMI_PS_Mort <- NSTEMI2 %>%
  select(DCB_DES, Age, Sex, PMHx_AF, FHx_CAD, Tash_Bif, Diffuse_Dx, Tortuosity, denovo_LesionLgth, denovo_VesselDiam, Mortality, Mortality_FU, Mortality_FU365, Mortality_365, Mortality_FU30, Mortality_30, CV_Mortality, CV_Mortality_FU, CV_Mortality_FU365, CV_Mortality_365, CV_Mortality_FU30,CV_Mortality_30, ACS, ACS_FU, ACS_FU365, ACS_365, ACS_FU30, ACS_30, TIA, TIA_FU, TIA_FU365, TIA_365, TIA_FU30, TIA_30, MajBleeding, MajBleeding_FU, MajBleeding_FU365, MajBleeding_365, MajBleeding_FU30, MajBleeding_30, Composite_wMort, Composite_wMort_FU, Composite_wMort_FU365, Composite_wMort_365, Composite_wMort_FU30, Composite_wMort_30) %>%
  drop_na(1:10)

set.seed(1234)

match.it <- matchit(DCB_DES ~ Age+ Sex + PMHx_AF+ FHx_CAD+ Tash_Bif+ Diffuse_Dx+ Tortuosity+ denovo_LesionLgth+ denovo_VesselDiam, data = NSTEMI_PS_Mort,  method="genetic", replace = T,  pop.size = 1000)
a <- summary(match.it)

df.match1 <- get_matches(match.it)

df.match1_LT65 <- df.match1
```

```{r MultiVariate Mortality PSMatched}
NSTEMI_Mort <- df.match_All %>%
  select(DCB_DES, Mortality, Mortality_FU) %>%
  drop_na()

res.cox1a <- coxph(Surv(time = Mortality_FU, event = Mortality) ~ DCB_DES, data =  NSTEMI_Mort)

MV_T <- tbl_regression(res.cox1a, 
               exponentiate = T, 
               #show_single_row = c(DCB_DES, Tash_Bif, PMHx_HF, FHx_CAD), 
              # label = list(DCB_DES ~ "DCB/DES",
                    #        PMHx_HF ~ "History of Heart Failure",
                    #        FHx_CAD ~ "Familt History of Coronary Artery Disease",
                      #      Tash_Bif ~ "Bifurcations",
                     #       Frailty_Sc ~ "Frailty Score",
                      #      Acuity_Sc ~ "Acuity Score")
              ) %>%
  bold_p() %>%
  modify_header(label = "All-Cause Mortality (Multivariate)") %>%
  add_n() %>%
  as_gt()

gtsave(MV_T, "UV_Tables/Univariate-Mortality-PS.html")

```

```{r Table 1 - PS Matched (Mortality)}

NSTEMI_Table <- df.match_All %>%
  select(-ends_with("Acuity"), -id, -subclass)

Baseline_T <- tbl_summary(NSTEMI_Table,
            by = DCB_DES) %>%
  add_p() %>%
  bold_p() %>%
  add_overall() %>%
  gtsummary::separate_p_footnotes() %>%
  as_gt() 

gtsave(Baseline_T, "Table1/BaselineT-PSMort.html")
```

```{r PS Matched CumHaz Plots All}
fit1<- survfit(Surv(time = Mortality_FU, event = Mortality) ~ DCB_DES, data = df.match_All)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = df.match_All)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = df.match_All)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = df.match_All)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = df.match_All)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = df.match_All)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched/PS_CumHazPlots.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = df.match_All)
plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = df.match_All)
plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = df.match_All)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = df.match_All)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = df.match_All)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = df.match_All)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched/PS_CumHazPlots365.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = df.match_All)
plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = df.match_All)
plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = df.match_All)
plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = df.match_All)
plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = df.match_All)
plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = df.match_All)
plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched/PS_CumHazPlots30.pdf",
         width = 6, height = 6, onefile = T)
print(plot1, newpage = F)
print(plot2)
print(plot3)
print(plot4)
print(plot5)
print(plot6)
dev.off()
```

```{r PS Matched CumHaz Plots Bifur T}
fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = df.match1_BifT)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = df.match1_BifT)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = df.match1_BifT)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = df.match1_BifT)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = df.match1_BifT)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = df.match1_BifT)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_BifT/PS_CumHazPlots_BifT.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
  
fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = df.match1_BifT)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = df.match1_BifT)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = df.match1_BifT)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = df.match1_BifT)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = df.match1_BifT)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = df.match1_BifT)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_BifT/PS_CumHazPlots_BifT_365.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = df.match1_BifT)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = df.match1_BifT)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = df.match1_BifT)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = df.match1_BifT)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = df.match1_BifT)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_BifT/PS_CumHazPlots_BifT_30.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot5)
print(ps_plot6)
dev.off()
```

```{r PS Matched CumHaz Plots Bifur F}
fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = df.match1_BifF)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = df.match1_BifF)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = df.match1_BifF)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = df.match1_BifF)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = df.match1_BifF)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = df.match1_BifF)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_BifF/PS_CumHazPlots_BifF.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
  
fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = df.match1_BifF)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = df.match1_BifF)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = df.match1_BifF)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = df.match1_BifF)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = df.match1_BifF)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = df.match1_BifF)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_BifF/PS_CumHazPlots_BifF_365.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = df.match1_BifF)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = df.match1_BifF)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = df.match1_BifF)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  


fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = df.match1_BifF)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = df.match1_BifF)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_BifF/PS_CumHazPlots_BifF_30.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot5)
print(ps_plot6)
dev.off()
```

```{r PS Matched CumHaz Plots GT3mm T}
fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_GT3mm_T/PS_CumHazPlots_GT3T.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
  
fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_GT3mm_T/PS_CumHazPlots_GT3T_365.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = df.match1_GT3mmT)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_GT3mm_T/PS_CumHazPlots_GT3T_30.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot5)
print(ps_plot6)
dev.off()
```

```{r PS Matched CumHaz Plots GT3mm F}
fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_GT3mm_F/PS_CumHazPlots_GT3F.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
  
fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_GT3mm_F/PS_CumHazPlots_GT3F_365.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = df.match1_GT3mmF)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_GT3mm_F/PS_CumHazPlots_GT3F_30.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
```

```{r PS Matched CumHaz Plots Male}
fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = df.match1_Male)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = df.match1_Male)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = df.match1_Male)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = df.match1_Male)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = df.match1_Male)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = df.match1_Male)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_Male/PS_CumHazPlots_Male.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
  
fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = df.match1_Male)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = df.match1_Male)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = df.match1_Male)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = df.match1_Male)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = df.match1_Male)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = df.match1_Male)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_Male/PS_CumHazPlots_Male_365.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = df.match1_Male)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = df.match1_Male)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = df.match1_Male)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = df.match1_Male)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = df.match1_Male)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = df.match1_Male)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_Male/PS_CumHazPlots_Male_30.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
```

```{r PS Matched CumHaz Plots Female}
fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = df.match1_Female)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = df.match1_Female)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = df.match1_Female)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = df.match1_Female)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = df.match1_Female)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = df.match1_Female)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_Female/PS_CumHazPlots_Female.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
  
fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = df.match1_Female)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = df.match1_Female)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = df.match1_Female)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = df.match1_Female)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = df.match1_Female)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = df.match1_Female)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_Female/PS_CumHazPlots_Female_365.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = df.match1_Female)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = df.match1_Female)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = df.match1_Female)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = df.match1_Female)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = df.match1_Female)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_Female/PS_CumHazPlots_Female_30.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot5)
print(ps_plot6)
dev.off()
```

```{r PS Matched CumHaz Plots GT65}
fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = df.match1_GT65)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = df.match1_GT65)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = df.match1_GT65)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = df.match1_GT65)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = df.match1_GT65)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = df.match1_GT65)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_GT65/PS_CumHazPlots_GT65.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
  
fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = df.match1_GT65)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = df.match1_GT65)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = df.match1_GT65)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = df.match1_GT65)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = df.match1_GT65)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = df.match1_GT65)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_GT65/PS_CumHazPlots_GT65_365.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = df.match1_GT65)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = df.match1_GT65)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = df.match1_GT65)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU30, MajBleeding_30) ~ DCB_DES, data = df.match1_GT65)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = df.match1_GT65)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU30, Composite_wMort_30) ~ DCB_DES, data = df.match1_GT65)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_GT65/PS_CumHazPlots_GT65_30.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
```

```{r PS Matched CumHaz Plots LT65}
fit1<- survfit(Surv(Mortality_FU, Mortality) ~ DCB_DES, data = df.match1_LT65)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU, CV_Mortality) ~ DCB_DES, data = df.match1_LT65)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU, ACS) ~ DCB_DES, data = df.match1_LT65)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU, MajBleeding) ~ DCB_DES, data = df.match1_LT65)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU, TIA) ~ DCB_DES, data = df.match1_LT65)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

fit6<- survfit(Surv(Composite_wMort_FU, Composite_wMort) ~ DCB_DES, data = df.match1_LT65)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_LT65/PS_CumHazPlots_LT65.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()
  
fit1<- survfit(Surv(Mortality_FU365, Mortality_365) ~ DCB_DES, data = df.match1_LT65)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU365, CV_Mortality_365) ~ DCB_DES, data = df.match1_LT65)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU365, ACS_365) ~ DCB_DES, data = df.match1_LT65)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit4<- survfit(Surv(MajBleeding_FU365, MajBleeding_365) ~ DCB_DES, data = df.match1_LT65)
ps_plot4 <- ggsurvplot(fit4, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Major Bleed", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU365, TIA_365) ~ DCB_DES, data = df.match1_LT65)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_m", legend.labs = c("DCB", "DES"), xlab = "Months Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 60.875, pval.coord = c(0,0.1), legend.title = "")  

fit6<- survfit(Surv(Composite_wMort_FU365, Composite_wMort_365) ~ DCB_DES, data = df.match1_LT65)
ps_plot6 <- ggsurvplot(fit6, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), xscale="d_y", legend.labs = c("DCB", "DES"), xlab = "Years Since Index Procedure", ylab = "Probability of Incurring Composite Endpoint", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 365.25, pval.coord = c(0,0.1), legend.title = "")

cairo_pdf(filename = "Cum_Haz_Plots_Matched_LT65/PS_CumHazPlots_LT65_365.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot4)
print(ps_plot5)
print(ps_plot6)
dev.off()

fit1<- survfit(Surv(Mortality_FU30, Mortality_30) ~ DCB_DES, data = df.match1_LT65)
ps_plot1 <-ggsurvplot(fit1, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of All-Cause Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit2<- survfit(Surv(CV_Mortality_FU30, CV_Mortality_30) ~ DCB_DES, data = df.match1_LT65)
ps_plot2 <-ggsurvplot(fit2, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Cardiovascular Mortality", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "") 

fit3<- survfit(Surv(ACS_FU30, ACS_30) ~ DCB_DES, data = df.match1_LT65)
ps_plot3 <- ggsurvplot(fit3, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Incurring ACS", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  

fit5<- survfit(Surv(TIA_FU30, TIA_30) ~ DCB_DES, data = df.match1_LT65)
ps_plot5 <- ggsurvplot(fit5, fun = "cumhaz", pval = TRUE, conf.int = TRUE,
           risk.table = T, risk.table.y.text.col = TRUE, ylim=c(0,0.3), legend.labs = c("DCB", "DES"), xlab = "Days Since Index Procedure", ylab = "Probability of Having a Stroke/TIA", palette = c("#fba30c", "#0077b8"), theme = "lancet", break.time.by	= 5, pval.coord = c(0,0.1), legend.title = "")  


cairo_pdf(filename = "Cum_Haz_Plots_Matched_LT65/PS_CumHazPlots_LT65_30.pdf",
         width = 6, height = 6, onefile = T)
print(ps_plot1, newpage = F)
print(ps_plot2)
print(ps_plot3)
print(ps_plot5)
dev.off()
```

